---
title: "W_UP_01"
author: "Lisa Davis"
date: "Summer 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

We are trying to find the average number of push ups, between skills players and line players. Is there a statistical difference in the average number of push ups between both positions?

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

The number of push ups is numerical, and the different position is categorical. The format i will be using is Num~Cat. We will also be using a box plot and a numerical summary for numerical descriptive results. At the end we will include a t-test.

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results


<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(pushups~position,data=mydata)
```

The box plot shows, the skill players did an average of 60 push ups, and the line position did an average of 20 pushups less.



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```

The numerical data shows that there is significant difference between the line players, and the skill players. The mean for the line players is 17, and the mean for the skill players is 50. The difference in mean is 33 pushups.



## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```

The t-test shows that there is an average pushups between line players, and skill players. The difference is 33 pushups more than line players. The 95 percent of the timethe skill players do betwwen 20 and 45 more pushups in two minutes, than the line players. The p-value is so small, it caused us to reject the null hypothesis. 

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The original question is who does more pushups on average skill players or line players, Is there a statistical difference? We have found there is a difference per line players, and skill players. The difference is about 95 percent of the time, the skill players do betwwen 20 and 45 more pushups in two minutes, than the line players. The p-value is so small, it caused us to reject the null hypothesis, we found that there is a statistical difference.
